Using forecasting models for new book publishing

### 2015-08-08 paper.tex
añadiendo los 5 métodos de predicción utilizados
añadiendo contenido

Sales forecasting in editorial industry is a very complex problem.
The main issue of this paper is to compute forecasting of the sales for new unpublished-books, for which no historical data is available.
Thus, this paper faces the new book publishing problem using different prediction methods and using as inputs the historical sales data related to other yet published books, and some descriptive variables relative to the new unpublished-book.

En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
Sin embargo, en el caso de nuevos libros, sólo ciertos datos descriptivos están disponibles.

@@

Sin embargo, existen otras variables externas que también afectan a las ventas de un nuevo libro.
Se trata de cuestiones como la estacionalidad, modas o promociones.
Estas otras variables no medibles y que los métodos de predicción clásicos no pueden procesar y que un experto debe tener en cuenta modificando la predicción ofrecida por el método automático.

@@

 % weka.classifiers.trees.M5P
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
 \item

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item

 % weka.classifiers.functions.SMOreg
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
 \item

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item

>>>>

Sales forecasting in editorial industry is a very complex problem.
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use.

The main issue of this paper is to compute forecasting of the sales for new unpublished-books, for which no historical data is available.
Thus, this paper faces the new book publishing problem using different prediction methods and using as inputs the historical sales data related to other yet published books, and some descriptive variables relative to the new unpublished-book.

En el caso de libros ya publicados, se dispone de datos históricos que ayudan a la generación de modelos predictivos. 
Sin embargo, en el caso de nuevos libros no hay datos históricos que ayuden a definir patrones, y sólo ciertos datos descriptivos están disponibles.

@@

Sin embargo, existen otras variables externas que también afectan a las ventas de un nuevo libro.
Se trata de cuestiones como la estacionalidad, modas o promociones.
Estas otras variables no medibles y que los métodos de predicción clásicos no pueden procesar y que un experto debe tener en cuenta modificando la predicción ofrecida por el método automático. 
Las empresas editoriales suelen finalmente definir reglas o índices para ajustar subjetivamente los resultados de predicción.

@@

 % weka.classifiers.trees.M5P
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/trees/M5P.html
 \item M5P trees

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item Linear Regression

 % weka.classifiers.functions.SMOreg
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/SMOreg.html
 \item Support Vector Machine for Regression (SMOreg)

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item K-nearest neighbours classifier (IBk)

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item Multilayer Perceptron
